Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2016-06-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added intro to Analysis Chapter
cleaned up equation format

@@

Ratio from heat flux from source fire data
vyto second item ignite
\begin{equation} \label{eq:second_item}
\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
\end{equation}
where $\dot{q}''$ is the heat flux per unit area kW/m$^2$, $\dot{Q}$ is the heat release rate (kW), $\chi_r$ is the radiative fraction, and $R$ = distance from the point source to the target (m).

Source fire plume temp and shape factor from vertical cylinder
\begin{equation}\label{eq:source_fire}
\dot{q}'' = \epsilon \sigma F_{12} T^4  \\
\end{equation}
where $\epsilon$ is the emissivity, $\sigma$ is the Stefan\-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$) and $F_{12}$ is the radiative shape factor.

>>>>

In this chapter the application of emprical algebraic fire characterizations will be examined. Two different types of applications will be used.  In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.  In the second case, the height of the thermal damage on the gypsum board will be examined.

Values generated in the bench scale experiments will be utilized as input to predict real scale results using the algorithms.  Then the predicted results will be compared with the full-scale experiment results.

@@

Ratio from heat flux from source fire data
vyto second item ignite
\begin{equation} \label{eq:second_item}
\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
\end{equation}

\begin{tabbing}
where: \=  \\

\> $\dot{q}''$ is the heat flux per unit area kW/m$^2$\\
\> $\dot{Q}$ is the heat release rate (kW) \\ 
\> $\chi_r$ is the radiative fraction \\
\> $R$ = distance from the point source to the target (m) \\
\end{tabbing}

Source fire plume temp and shape factor from vertical cylinder
\begin{equation}\label{eq:source_fire}
\dot{q}'' = \epsilon \sigma F_{12} T^4  \\
\end{equation}

\begin{tabbing}
where: \=  \\
\> $\epsilon$ is the emissivity  \\
\> $\sigma$ is the Stefan-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$)  \\
\> $F_{12}$ is the radiative shape factor \\
\end{tabbing}
